Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-12 bbbq_article.tex
Use all software

\paragraph{Introduction}

@@

\paragraph{Data}

@@

\paragraph{Data retrieval}

@@

\paragraph{Pipeline}

@@

\begin{table}[]
  \begin{tabular}{llll}
    Goal & Tool & Reference \\ 
    \hline
    Predict topology                  & TMHMM                     & \cite{krogh2001predicting} \\
    Predict topology                  & PureseqTM                 & \cite{wang2019efficient} \\
    Predict epitopes MHC-I            & \verb;epitope-prediction; & \cite{bianchi2017} \\
    Predict epitopes MHC-II           & NetMHCIIpan               & \cite{nielsen2008quantitative,karosiene2013netmhciipan} \\
    Call TMHMM from R                 & tmhmm                     & \cite{tmhmm} \\
    Call PureseqTM from R             & pureseqtmr                & \cite{pureseqtmr} \\
    Call NetMHCIIpan from R           & netmhc2pan                & \cite{netmhc2pan} \\
    \verb;epitope-prediction; LUT     & epiprepreds               & \cite{epiprepreds} \\
    NetMHCIIpan LUT                   & nmhc2ppreds               & \cite{nmhc2ppreds} \\
    Sequence alignment                & ClustalW                  & \cite{thompson1994clustal} \\
    Conservation scores               & msa                       & \cite{bodenhofer2015msa} \\
    Combine all                       & bbbq                      & \cite{bbbq}
  \end{tabular}
  \caption{
    Overview of all software used in this research.
    'LUT' is an abbreviation for 'Look-up table'. 
  }
  \label{table:software_used}
\end{table}

@@

\paragraph{TMH prediction}

@@

\paragraph{MHC-I epitope prediction}

@@

\paragraph{MHC-II epitope prediction}

@@

The R programming language is used for the complete 
experiment, including the analysis.
The complete experiment is bundled in the 'bbbq' R package,
which is dependent on 'pureseqtmr', 
'epitope-prediction' and 'epiprepreds',
'netmhc2pan' and 'nmhc2ppreds'
as described below.

To be able to call, from R, the TMH prediction software 'PureseqTM',
which is written in C, the package 'pureseqtmr' has been developed. 
'pureseqtmr' allows to install 'PureseqTM' and use most of its features.
Excluded are the features that are used by the 'PureseqTM' 
developers to verify the correctness of their work.
'pureseqtmr' has been submitted to CRAN.

To be able to use pre-calculated 
\verb;epitope-prediction; and NetMHCIIpan
predictions (i.e. a distribution of IC50 values per haplotype, 
derived from random peptides), the 'epiprepreds' and 'nmhc2ppreds' 
R packages have been 
developed. In practice, these are nothing more than a big look-up table.
If \verb;epitope-prediction; is put onto CRAN, 'epiprepreds'
will be submitted as well.
If 'netmhc2pan' is allowed onto CRAN, 'nmhc2ppreds'
will be submitted as well.

>>>>

% \paragraph{Introduction}

@@

% \paragraph{Data}

@@

% \paragraph{Data retrieval}

@@

% \paragraph{Pipeline}

@@

\begin{table}[]
  \begin{tabular}{llll}
    Goal & Tool & Reference \\ 
    \hline
    Predict topology                  & TMHMM                     & \cite{krogh2001predicting} \\
    Predict topology                  & PureseqTM                 & \cite{wang2019efficient} \\
    Predict epitopes MHC-I            & \verb;epitope-prediction; & \cite{bianchi2017} \\
    Predict epitopes MHC-II           & NetMHCIIpan               & \cite{nielsen2008quantitative,karosiene2013netmhciipan} \\
    Call TMHMM from R                 & tmhmm                     & \cite{tmhmm} \\
    Call PureseqTM from R             & pureseqtmr                & \cite{pureseqtmr} \\
    Call NetMHCIIpan from R           & netmhc2pan                & \cite{netmhc2pan} \\
    Combine all                       & bbbq                      & \cite{bbbq}
  \end{tabular}
  \caption{
    Overview of all software used in this research.
    'LUT' is an abbreviation for 'Look-up table'. 
  }
  \label{table:software_used}
\end{table}

@@

% \paragraph{TMH prediction}

@@

% \paragraph{MHC-I epitope prediction}

@@

% \paragraph{MHC-II epitope prediction}

@@

The R programming language is used for the complete 
experiment, including the analysis.
The complete experiment is bundled in the 'bbbq' R package,
which is dependent on 'tmhmm', 'pureseqtmr', 
'epitope-prediction' and 'mhcnuggetsr'
as described below.

% \paragraph{tmhmm}

The R package 'tmhmm' was developed to do the same topology
predictions as the earlier study (that used 'TMHMM'), yet in a reproducible way.
'TMHMM' has a restrictive software license and allows a user
to download a pre-compiled executable after confirmation he/she
is in academia. The R package respects this restriction
and allows the user to install and use TMHMM from within R,
as done in this study.
'tmhmm' has been submitted to and is accepted by CRAN.

% \paragraph{pureseqtmr}

To be able to call, from R, the TMH prediction software 'PureseqTM',
which is written in C, the package 'pureseqtmr' has been developed. 
'pureseqtmr' allows to install 'PureseqTM' and use most of its features.
Excluded are the features that are used by the 'PureseqTM' 
developers to verify the correctness of their work.
'pureseqtmr' has been submitted to and is accepted by CRAN.

% \paragraph{mhcnuggetsr}

MHCnuggets is a free and open-source Python package to predict 
epitope affinity for many MHC-I and MHC-II variants.
The R package 'mhcnuggetsr' allows one to install and use MHCnuggets
from within R.
Also 'mhcnuggetsr' has been submitted to and is accepted by CRAN.

% \paragraph{bbbq}
